The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-06-03 paper/paper.tex

In summary: metacal allows us to correct for significant selection biases, but only if all selections
are performed using only bands in which the PSF is measured well enough for deconvolution to be
performed.  For Rubin, this means using only the $r$, $i$, $z$, and perhaps $g$ bands.  In this work we
therefore study how well we can perform tomography using only this limited photometric information.  In
particular, this limitation prevents us from using the most obvious method for tomography,
and computing a complete photometric probability density function (PDF) for each galaxy and assigning
a bin using the mean or peak of that PDF\footnote{This only prevents us using other photometry for \emph{selection}, not for \emph{characterization} after objects have been selected, such as computing the overall
number density $n(z)$ for a tomographic bin.}.

>>>>

In summary: metacal allows us to correct for significant selection biases, but only if all selections
are performed using only bands in which the PSF is measured well enough for deconvolution to be
performed\footnote{Alternative or extended methods to the metacalibration process described here, modelling the full likelihood space of deconvolved galaxy properties in a unified way might one day be feasible, but are likely to be computationally challenging.}.  For Rubin, this means using only the $r$, $i$, $z$, and perhaps $g$ bands.  In this work we
therefore study how well we can perform tomography using only this limited photometric information.  In
particular, this limitation prevents us from using the most obvious method for tomography,
and computing a complete photometric probability density function (PDF) for each galaxy and assigning
a bin using the mean or peak of that PDF\footnote{This only prevents us using other photometry for \emph{selection}, not for \emph{characterization} after objects have been selected, such as computing the overall
number density $n(z)$ for a tomographic bin.}.
